The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2024-03-27 MS_ToSubmit/RevisedVersion_1.Rmd
Update listings package

---
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
bibliography: AMPBancoBurdwood.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

>>>>

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
bibliography: AMPBancoBurdwood.bib
csl: "elsevier-harvard2.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{amsmath}
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \usepackage{listings}
- \linenumbers
---
